---
title: "Week 2 Assignment"
output: html_document
---
###SQL and R
####Elina Azrilyan
####8 September 2018

Choose six recent popular movies. Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5. Take the results (observations) and store them in a SQL database. Load the information into an R dataframe.

Your deliverables should include your SQL scripts and your R Markdown code, posted to GitHub. This is by design a very open ended assignment. A variety of reasonable approaches are acceptable. You can (and should) blank out your SQL password if your solution requires it; otherwise, full credit requires that your code is “reproducible,” with the assumption that I have the same database server and R software. You may work in a small group.
```{r}
# loading package
# install.packages("RMySQL")
# install.packages("dplyr")
library(RMySQL)
```
#####Establish connection
```{r}
con <- dbConnect(MySQL(), user='root', password='root', dbname='MR', host='localhost')
```
#####Run a query to create a table which now contains the summary of movies and their respective ratings
```{r}
mr <- dbGetQuery(con, "SELECT m.movieid AS ID, m.movietitle AS Title, m.releaseyear AS 'Year', m.genre AS Genre, m.rtscore AS 'RTScore', r.friendname, r.friendrating
  FROM Movies m
    INNER JOIN Ratings r ON m.movieid = r.movieid
  ORDER BY m.movieid;")

# Disconecting from Database
dbDisconnect(con)

head(mr)
```

#####Calculate average movie rating based on opinion of my friends. RTScore = Rotten Tomatoes Score. 
```{r message=FALSE}
library(dplyr)
newmr <- mr %>%
 group_by(Title,Year, Genre, RTScore) %>%
 summarise(AvgRating = mean(friendrating))
newmrframe <- as.data.frame(newmr)
newmrframe
```
#####Let's convert Rotten Tomatoes Score to a 5 point scale to make comparison easier.
```{r}
newmrframe$RTScoreConv<-newmrframe$RTScore/100*5
newmrframe
```

######The obvious difference in scores is due to the sample size I was using. A sample size of 5 is clearly not large enough. Opinion of 1 person can skew the results where significantly. 

#####Let's identify which genre my friends prefer.
```{r}
newmrfriend <- mr %>%
 group_by(Genre) %>%
 summarise(AvgRating = mean(friendrating))
newmrfriendframe <- as.data.frame(newmrfriend)
newmrfriendframe
```
#####My friends seem to prefer Drama.

#####Let's identify who is the harshest critic.
```{r}
newmrcr <- mr %>%
 group_by(friendname) %>%
 summarise(AvgRating = round(mean(friendrating), digits = 2))
newmrcrframe <- as.data.frame(newmrcr)
newmrcrframe
```
#####Not surprisingly, my picky friend Lilya is showing the lowest average results and Andrey who likes Action movies is showing the highest score (3 out of 6 films were from that Genre).
